\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-15 paper.qmd
Find the best and the worst models

Projections of the $7\text{-}D$ S-curve data (purple points) overlaid with the model (black grid with  green points indicating bin means) constructed from the UMAP layout, with XXX bins (using the **langevitour** software). The model closely fits the shape of this data. A video of the full tour is available at (<https://youtu.be/G1m4q9k--v4>).
:::

>>>>

Projections of the $7\text{-}D$ S-curve data (purple points) overlaid with the model (black grid with  green points indicating bin means) constructed from the UMAP layout, with 48 non-empty bins (using the **langevitour** software). The model closely fits the shape of this data. A video of the full tour is available at (<https://youtu.be/G1m4q9k--v4>).
:::

### 2024-06-15 paper.tex
Find the best and the worst models

\caption{\label{fig-scurve-sc}Projections of the \(7\text{-}D\) S-curve
data (purple points) overlaid with the model (black grid with green
points indicating bin means) constructed from the UMAP layout, with XXX
bins (using the \textbf{langevitour} software). The model closely fits
the shape of this data. A video of the full tour is available at
(\url{https://youtu.be/G1m4q9k--v4}).}

>>>>

\caption{\label{fig-scurve-sc}Projections of the \(7\text{-}D\) S-curve
data (purple points) overlaid with the model (black grid with green
points indicating bin means) constructed from the UMAP layout, with 48
non-empty bins (using the \textbf{langevitour} software). The model
closely fits the shape of this data. A video of the full tour is
available at (\url{https://youtu.be/G1m4q9k--v4}).}
